\section{Movement}
This section defines the movement of the mesh. Currently only static
non-conformal interfaces are supported.

\subsection{Non-conformal meshes}\label{subsec:non-conformal-meshes}
Non-conformal meshes are defined using \inltt{ZONES} and \inltt{INTERFACES}.
Each zone is a domain as defined in the \inltt{GEOMETRY} section. For a mesh to
be non-conformal it must consist of at least two zones with different domain
tags. These two zones can then be split by an interface where every interface is
defined by two composite entities, we use \inltt{LEFT} and \inltt{RIGHT}
notation to distinguish between these. Each zone must contain either the left or
the right interface edge. Zones can contain multiple edges across different
interfaces but must not contain both edges for the same interface. These left
and right interface edges have to be geometrically identical but topologically
disconnected i.e.\ occupy the same space physically but consist of independent
geometry objects.

Non-conformal interfaces are defined enclosed in the \inltt{NEKTAR} tag. An
example showing two non-conformal interfaces on a single mesh is below:

\begin{lstlisting}[style=XMLStyle]
<MOVEMENT>
    <ZONES>
        <FIXED ID="0" DOMAIN="D[0]" />
        <FIXED ID="1" DOMAIN="D[1]" />
        <FIXED ID="2" DOMAIN="D[2]" />
    </ZONES>
    <INTERFACES>
        <INTERFACE NAME="First">
            <LEFT  ID="0" BOUNDARY="C[0]" />
            <RIGHT ID="1" BOUNDARY="C[1]"  />
        </INTERFACE>
        <INTERFACE NAME="Second">
            <LEFT  ID="1" BOUNDARY="C[2]" />
            <RIGHT ID="2" BOUNDARY="C[3]"  />
        </INTERFACE>
    </INTERFACES>
</MOVEMENT>
\end{lstlisting}

Zones must have a type specified, at the moment only `FIXED' interfaces are
supported however in the future there are plans to implement rotating, sliding,
and prescribed motion using the ALE method. It is important for the zone IDs to
correspond with the relevant interface IDs present on the zone, that is if there
is an interface with ID 0 there must also be a zone with ID 0 too. Zone IDs must
be unique but interfaces can have the same ID, e.g. in the example above zone ID
1 has two interfaces attached to it. The inclusion of an
\inltt{"INTERFACE NAME="..."} allows for specifying a name, which is used for
the debug output when the verbose flag `-v' is specified. This is for user
reference to ensure the non-conformal interfaces are set up correctly, and shows
zone/interface IDs, number of elements in each zone and interface, and
connections between each zone/interface. An example debug output for the above
XML is shown below:

\begin{lstlisting}
Movement Info:
	Num zones: 3
	- 0 Fixed: 8  Quadrilaterals
	- 1 Fixed: 24 Quadrilaterals
	- 2 Fixed: 4  Quadrilaterals
	Num interfaces: 2
	- "First":  0 (4 Segments) <-> 1 (6 Segments)
	- "Second": 1 (6 Segments) <-> 2 (2 Segments)
\end{lstlisting}